\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-10-09 coqimpl.tex
Enhacning Compilation Code Example.

\begin{figure}[!htb]
  \begin{minipage}[t]{0.32\linewidth}
\begin{lstlisting}[language=Coq,  escapeinside={@}{@}]
Family STLC.
  FInductive tm : Set := ... 
  FScheme tm_prec PRecT about self__STLC.tm.
  FScheme Comp about self__STLC.tm_prec.
  (* Generate Partial Recursor 
  and the computational axiom *)
  Family subst_internal. 
  Final Field tm_var : ...
:= fun s x t => 
    if (eqb x s) 
    then t else (tm_var s).
  Final Field tm_abs : ...
:= fun s (b : tm)   
   (recb : id → tm → tm) 
   x t => 
    if (eqb x s) 
    then (tm_abs s body)
    else (tm_abs s (recb x t)).
(* ... *)
  EndFamily.
  FRecursor subst 
    about tm 
    motive (fun _ => id → tm → tm)
    using subst_internal
    by _rec.
(* Field test := (subst (tm_var 0) 0 (tm_var 0)).@\YZ{Why is "test" commented out?}\EDJreply{Because I want to show I can do it but I don't really want to d -- if I really do it the compilation result shown later will need to have this information.}@ *)
(* ... *)
EndFamily.
Family STLC_bool extends STLC.
(* ... *)
Extend FInductive tm : Set :=
  | tm_true : tm ...
Extend Family subst_internal.
Final Field tm_true : ...
  := fun x t => tm_true.
(* ... *)
EndFamily. 
Inherits subst.
(* ... *)
EndFamily.
\end{lstlisting}
  \end{minipage}
  \begin{minipage}[t]{0.65\linewidth}
\begin{minted}[fontsize=\footnotesize,escapeinside=@@]{Coq}
Module Type STLC_Interface.
  Parameter (tm : Set).
  Parameter (tm_var : id → tm).
  Parameter (tm_abs : id → tm → tm).
  (* ... and all the fields defined before
  and the abstraction for inductive type ...*)
End STLC_Interface.
(* Collect eliminator to Set for tm *)
Module tm_rec_type (STLC: STLC_Interface).
  Definition __recursor_type_tm_rec :=
    forall P : STLC.tm -> Set,
    (forall n : id, P (STLC.tm_var n)) ->
    (forall (n : id) (i : STLC.tm),
    P i -> P (STLC.tm_abs n i)) ->
    ... -> forall i : STLC.tm, P i.
End tm_rec_type.
(* Compiled Field STLC.subst_internal.tm_var *)
Module tm_var_handle (self__STLC: STLC_Interface)
  (self__subst_internal: EmptySig_84).
Definition tm_var :
  forall (s : ident) (x : ident) (t : self__STLC.tm), self__STLC.tm :=
  fun s x t => if eqb x s then t else self__STLC.tm_var s.
End tm_var_handle. (* ... and more *)
(* Assembling STLC.subst_internal when compilation *)
Module subst_internal_410 (STLC: STLC_Interface). 
  Module subst_internal.
  Include tm_var_handle STLC. Include tm_abs_handle STLC.
  Include tm_app_handle STLC. Include tm_unit_handle STLC.
  End subst_internal.
End subst_internal_410.
Module do_tc (STLC: STLC_Interface).
(* Intermediate Module solely for type checking *)
  Include tm_rec_type STLC.
  Parameter (recursor_for_type_checking : __recursor_type_tm_rec).
  Definition term_for_type_checking :=
    recursor_for_type_checking (fun _  ⇒ id → STLC.tm → STLC.tm)
      subst_internal_410.tm_var
      subst_internal_410.tm_abs ... .
End do_tc.
(* Ctx that expose concrete inductive type *)
Module Type ctx_subst_113.
Inductive __internal_tm : Set := ... 
Include subst_internal_410. (* ... and more inclusion *)
End ctx_subst_113.
(* Compilation of recursor, not reusable
    when inductive type extended due to the ctx *)
Module subst_128 (self__STLC: ctx_subst_113).
Include __motive_of_subst_107 self__STLC.
Definition subst :=
  self__STLC.__internal_tm_rec __motiveTsubst
	self__STLC.subst_internal.tm_var self__STLC.subst_internal.tm_abs
    self__STLC.subst_internal.tm_app self__STLC.subst_internal.tm_unit.
End subst_128.
(* Assembling the whole STLC *)
Module STLC.
Include tm_5. Include tm_prec_72. Include tm_prectm_81.
Include subst_internal_410. Include subst_128.
End v_129.
(* Assembling STLC_bool.subst_internal via reusing 
    most of the former compilation results *)
Module subst_internal_248 (STLC_bool: STLC_Interface).
Include tm_true_197 STLC_bool.
Include tm_false_200 STLC_bool.
Include tm_if_203 STLC_bool.
(* The Reused Compilation result *)
Include tm_var_handle STLC_bool.
Include tm_abs_handle STLC_bool.
Include tm_app_handle STLC_bool.
Include tm_unit_handle STLC_bool.
End v_248.
@\YZ{It'd be useful to (1) show how the parts of the STLC family are assembled and recursor inserted, and (2) show the code compiled for STLC\_bool and how code from STLC is shared with STLC\_bool.}@
\end{minted}
  \end{minipage}
\caption{Exemplar STLC Code, especially about Inductive Type}\label{fig:plugin-example2}
\end{figure}

>>>>

% \begin{figure}[!htb]
%   \begin{minipage}[t]{0.32\linewidth}
% \begin{lstlisting}[language=Coq,  escapeinside={@}{@}]
% Family STLC.
%   FInductive tm : Set := tm_var : ... 
%   FScheme tm_prec PRecT about self__STLC.tm.
%   FScheme Comp about self__STLC.tm_prec.
%   (* Generate Partial Recursor 
%   and the computational axiom *)
%   Family subst_internal. 
%   Final Field tm_var : ...
% := fun s x t => 
%     if (eqb x s) 
%     then t else (tm_var s).
% (* ... other three cases *)
%   EndFamily.
%   FRecursor subst 
%     about tm 
%     motive (fun _ => id → tm → tm)
%     using subst_internal
%     by _rec.
% (* Field test := (subst (tm_var 0) 0 (tm_var 0)).@\YZ{Why is "test" commented out?}\EDJreply{Because I want to show I can do it but I don't really want to d -- if I really do it the compilation result shown later will need to have this information.}@ *)
% (* ... *)
% EndFamily.
% Family STLC_bool extends STLC.
% (* ... *)
% Extend FInductive tm : Set :=
%   | tm_true : tm ...
% Extend Family subst_internal.
% Final Field tm_true : ...
%   := fun x t => tm_true.
% (* ... *)
% EndFamily. 
% Inherits subst.
% (* ... *)
% EndFamily.
% \end{lstlisting}
%   \end{minipage}
%   \begin{minipage}[t]{0.65\linewidth}
% \begin{minted}[fontsize=\footnotesize,escapeinside=@@]{Coq}
% Module Type STLC_Interface.
%   Parameter (tm : Set).
%   Parameter (tm_var : id → tm).
%   Parameter (tm_abs : id → tm → tm).
%   (* ... and all the fields defined before
%   and the abstraction for inductive type ...*)
% End STLC_Interface.
% (* Collect eliminator to Set for tm *)
% Module tm_rec_type (STLC: STLC_Interface).
%   Definition __recursor_type_tm_rec :=
%     forall P : STLC.tm -> Set,
%     (forall n : id, P (STLC.tm_var n)) ->
%     (forall (n : id) (i : STLC.tm),
%     P i -> P (STLC.tm_abs n i)) ->
%     ... -> forall i : STLC.tm, P i.
% End tm_rec_type.
% (* Compiled Field STLC.subst_internal.tm_var *)
% Module tm_var_handle (self__STLC: STLC_Interface)
%   (self__subst_internal: EmptySig_84).
% Definition tm_var :
%   forall (s : ident) (x : ident) (t : self__STLC.tm), self__STLC.tm :=
%   fun s x t => if eqb x s then t else self__STLC.tm_var s.
% End tm_var_handle. (* ... and more *)
% (* Assembling STLC.subst_internal when compilation *)
% Module subst_internal_410 (STLC: STLC_Interface). 
%   Module subst_internal.
%   Include tm_var_handle STLC. Include tm_abs_handle STLC.
%   Include tm_app_handle STLC. Include tm_unit_handle STLC.
%   End subst_internal.
% End subst_internal_410.
% Module do_tc (STLC: STLC_Interface).
% (* Intermediate Module solely for type checking *)
%   Include tm_rec_type STLC.
%   Parameter (recursor_for_type_checking : __recursor_type_tm_rec).
%   Definition term_for_type_checking :=
%     recursor_for_type_checking (fun _  ⇒ id → STLC.tm → STLC.tm)
%       subst_internal_410.tm_var ... .
% End do_tc.
% (* Ctx that expose concrete inductive type *)
% Module Type ctx_subst_113.
% Inductive __internal_tm : Set := ... 
% Include subst_internal_410. (* ... and more inclusion *)
% End ctx_subst_113.
% (* Compilation of recursor, not reusable
%     when inductive type extended due to the ctx *)
% Module subst_128 (self__STLC: ctx_subst_113).
% Include __motive_of_subst_107 self__STLC.
% Definition subst :=
%   self__STLC.__internal_tm_rec __motiveTsubst
% 	self__STLC.subst_internal.tm_var ... .
% End subst_128.
% (* Assembling the whole STLC *)
% Module STLC.
% Include tm_5. Include tm_prec_72. Include tm_prectm_81.
% Include subst_internal_410. Include subst_128.
% End v_129.
% (* Assembling STLC_bool.subst_internal via reusing 
%     most of the former compilation results *)
% Module subst_internal_248 (STLC_bool: STLC_Interface).
% Include tm_true_197 STLC_bool. Include ...
% (* The Reused Compilation result *)
% Include tm_var_handle STLC_bool. Include ...
% End v_248.
% @\YZ{It'd be useful to (1) show how the parts of the STLC family are assembled and recursor inserted, and (2) show the code compiled for STLC\_bool and how code from STLC is shared with STLC\_bool.}@
% \end{minted}
%   \end{minipage}
% \caption{Exemplar STLC Code, especially about Inductive Type}\label{fig:plugin-example2}
% \end{figure}
\include{ext-ind-type-compilation-example.tex}
